---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# `{xmrnetscan}`

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

`{xmrnetscan}` is an alpha project. Expect breaking changes in future versions.

## Installation

You can install the development version of `{xmrnetscan}` like so:

Install R. Linux users should install the `r-base` and `r-base-dev` system packages.

You can install the development version of `{xmrnetscan}` from [GitHub](https://github.com/) if you have `git` and `curl` installed on your system with:

```{r, eval = FALSE}
install.packages("remotes")
remotes::install_github("Rucknium/xmrnetscan", upgrade = FALSE)
```

## Run

You can launch the application by running:

```{r, eval = FALSE}
xmrnetscan::run_app()
```
